The Rockerverse: Packages and Applications for Containerisation with R

### 2020-03-09 rockerverse.Rmd
Add NR support to awknowledgements
use citation for dynverse

@@

\citet{gentleman_statistical_2007} coined the term **Research Compendium** for a dynamic document together with supporting data and code.
They used the R package system \citep{core_writing_1999} for the functional prototype all the way to structuring, validating, and distributing research compendia.
This concept has been taken up and extended\footnote{See full literature list at \href{https://research-compendium.science/}{https://research-compendium.science/}.}, not in the least by applying containerisation and other methods for managing computing environments---see Section&nbsp;\nameref{envs}.
Containers give the researcher an isolated environment to assemble these research pipelines with specific versions of software to minimize problems with breaking changes and make workflows easier to share \citep[cf.][]{boettiger_introduction_2015,marwick_packaging_2018}.
Research workflows in containers are safe from contamination from other activities that occur on the researcher's computer, for example the installation of newest version of packages for teaching demonstrations or specific versions for evaluation of others' works.
Given the users in this scenario, i.e., often academics with limited formal software development training, templates and assistance with containers around research compendia is essential.
In many fields we see that a typical unit of research for a container is a research report or journal article, where the container holds the compendium, or self-contained set of data (or connections to data elsewhere) and code files needed to fully reproduce the article \citep{marwick_packaging_2018}.
The package \pkg{rrtools} ([https://github.com/benmarwick/rrtools](https://github.com/benmarwick/rrtools)) provides a template and convenience functions to apply good practices for research compendia, including a starter `Dockerfile`.
Images of compendium containers can be hosted on services such as Docker&nbsp;Hub for convenient sharing among collaborators and others.
Similarly, packages such as \pkg{containerit} and \pkg{dockerfiler} can be used to manage the `Dockerfile` to be archived with a compendium on a data repository (e.g. [Zenodo](https://zenodo.org/), [Dataverse](https://dataverse.org/), [Figshare](https://figshare.com/), [OSF](https://osf.io/)).
A typical compendium's `Dockerfile` will pull a rocker image fixed to a specific version of R, and install R packages from the MRAN repository to ensure the package versions are tied to a specific date, rather than the most recent version.
A more extreme case is the _dynverse_ project ([https://dynverse.org/](https://dynverse.org/)), which packages over 50 computational methods with different environments (R, Python, C++, etc.) in Docker images, which can be executed from R.
_dynverse_ uses a CI platform (see&nbsp;\nameref{ci}) to build Rocker-derived images, test them, and, if the tests succeed, publish them on Docker&nbsp;Hub.

@@

DN is supported by the project Opening Reproducible Research ([o2r](https://www.uni-muenster.de/forschungaz/project/12343)) funded by the German Research Foundation (DFG) under project number [PE&nbsp;1632/17-1](https://gepris.dfg.de/gepris/projekt/415851837).
The funders had no role in data collection and analysis, decision to publish, or preparation of the manuscript.
KR was supported in part  by a grant from The Leona M. and Harry B. Helmsley Charitable Trust, award number 2016PG-BRI004.
LS and NT are supported by US NIH / NHGRI awards U41HG00405 and U24HG010263.
CW is supported by the Whole Tale project (https://wholetale.org) funded by the US National Science Foundation (NSF) under award [OAC-1541450](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1541450).
We would like to thank Celeste R. Brennecka from the Science Writing Support Service of the University of Münster for her editorial support.

>>>>

    # https://github.com/MarkEdmondson1234

@@

\citet{gentleman_statistical_2007} coined the term **Research Compendium** for a dynamic document together with supporting data and code.
They used the R package system \citep{core_writing_1999} for the functional prototype all the way to structuring, validating, and distributing research compendia.
This concept has been taken up and extended\footnote{See full literature list at \href{https://research-compendium.science/}{https://research-compendium.science/}.}, not in the least by applying containerisation and other methods for managing computing environments---see Section&nbsp;\nameref{envs}.
Containers give the researcher an isolated environment to assemble these research pipelines with specific versions of software to minimize problems with breaking changes and make workflows easier to share \citep[cf.][]{boettiger_introduction_2015,marwick_packaging_2018}.
Research workflows in containers are safe from contamination from other activities that occur on the researcher's computer, for example the installation of newest version of packages for teaching demonstrations or specific versions for evaluation of others' works.
Given the users in this scenario, i.e., often academics with limited formal software development training, templates and assistance with containers around research compendia is essential.
In many fields we see that a typical unit of research for a container is a research report or journal article, where the container holds the compendium, or self-contained set of data (or connections to data elsewhere) and code files needed to fully reproduce the article \citep{marwick_packaging_2018}.
The package \pkg{rrtools} ([https://github.com/benmarwick/rrtools](https://github.com/benmarwick/rrtools)) provides a template and convenience functions to apply good practices for research compendia, including a starter `Dockerfile`.
Images of compendium containers can be hosted on services such as Docker&nbsp;Hub for convenient sharing among collaborators and others.
Similarly, packages such as \pkg{containerit} and \pkg{dockerfiler} can be used to manage the `Dockerfile` to be archived with a compendium on a data repository (e.g. [Zenodo](https://zenodo.org/), [Dataverse](https://dataverse.org/), [Figshare](https://figshare.com/), [OSF](https://osf.io/)).
A typical compendium's `Dockerfile` will pull a rocker image fixed to a specific version of R, and install R packages from the MRAN repository to ensure the package versions are tied to a specific date, rather than the most recent version.
A more extreme case is the _dynverse_ project \citep{saelens_comparisonsinglecelltrajectory_2019}, which packages over 50 computational methods with different environments (R, Python, C++, etc.) in Docker images, which can be executed from R.
_dynverse_ uses a CI platform (see&nbsp;\nameref{ci}) to build Rocker-derived images, test them, and, if the tests succeed, publish them on Docker&nbsp;Hub.

@@

DN is supported by the project Opening Reproducible Research ([o2r](https://www.uni-muenster.de/forschungaz/project/12343)) funded by the German Research Foundation (DFG) under project number [PE&nbsp;1632/17-1](https://gepris.dfg.de/gepris/projekt/415851837).
The funders had no role in data collection and analysis, decision to publish, or preparation of the manuscript.
KR was supported in part  by a grant from The Leona M. and Harry B. Helmsley Charitable Trust, award number 2016PG-BRI004.
LS and NT are supported by US NIH / NHGRI awards U41HG00405 and U24HG010263.
CW is supported by the Whole Tale project (https://wholetale.org) funded by the US National Science Foundation (NSF) under award [OAC-1541450](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1541450).
NR is supported in part by the Chan-Zuckerberg Initiative Essential Open Source Software for Science program.
We would like to thank Celeste R. Brennecka from the Science Writing Support Service of the University of Münster for her editorial support.
